\tableListofDeliverables{
3.3 D1 & Software published and report submitted to project coordinator. & WP3 & DEB & OTHER & PU & 32\\\hline
1.4 D2 & Scholarly publication on context-aware recommendation system. & WP1 & BEL & R & PU & 14\\\hline
1.4 D1 & Scholarly publication on technology enhanced learning. & WP1 & BEL & R & PU & 13\\\hline
5.5 D1 & Workshop report submitted to project coordinator & WP5 & ITR & DEM & PU & 20\\\hline
1.1 D2 & Scholarly publication on the architecture of the infrastructure. & WP1 & DEB & R & PU & 12\\\hline
1.3 D1 & Technical report on Blockchain security submitted to project coordinator. & WP1 & RSB & R & PU & 12\\\hline
6.1 D1 & Project progress reports & WP6 & DEB & R & SEN & 3\\\hline
4.1 D1 & An online software platform with integrated data processing tools & WP4 & DEB & OTHER & SEN & 11\\\hline
3.1 D1 & Website launched & WP3 & DEB & DEC & PU & 9\\\hline
3.1 D2 & Website launched AAA & WP3 & DEB & DEC & PU & 9\\\hline
2.3 D1 & Data uploaded and internal report submitted to project coordinator. & WP2 & HUM & DATA & PU & 12\\\hline
2.2 D1 & Internal report submitted to project coordinator. & WP2 & DEB & R & SEN & 12\\\hline
3.2 D1 & Algrithm developed and supbmitted to project coordinator. & WP3 & DEB & OTHER & SEN & 30\\\hline
2.1 D1 & Scientific publication on novel diagnostic techniques. & WP2 & ITP & R & PU & 22\\\hline
5.2 D1 & Workshop report submitted to project coordinator & WP5 & BAS & DEM & PU & 20\\\hline
2.2 D2 & First version of the portal published for testing. & WP2 & DEB & DEC & PU & 20\\\hline
5.1 D1 & Workshop report submitted to project coordinator & WP5 & DEB & DEM & PU & 20\\\hline
5.4 D1 & Workshop report submitted to project coordinator & WP5 & SKB & DEM & PU & 20\\\hline
1.2 D1 & Technical report on informatics tool submitted to project coordinator. & WP1 & SKB & R & PU & 12\\\hline
5.3 D1 & Workshop report submitted to project coordinator & WP5 & CZU & DEM & PU & 20\\\hline
1.1 D1 & Technical report on cloud ecosystem submitted to project coordinator. & WP1 & DEB & R & PU & 12\\\hline
5.7 D1 & Workshop report submitted to project coordinator & WP5 & DEB & DEM & PU & 20\\\hline
5.6 D1 & Workshop report submitted to project coordinator & WP5 & HUM & DEM & PU & 20\\\hline
6.2 D1 & Annual reports and the final project report to the EU. & WP6 & DEB & R & SEN & 36\\\hline
}

