\textbf{Objectives}\\
The cultural heritage research is information, event and context driven activity to gain valuable insights for restoration, discovery, and promotion of artefacts. Our proposed cloud provides ability to create, update, restore, reuse, move, migrate, transform, contextualise, and manage data and information in a secured manner with ease and affordability. It enables on-demand reusability of component and services. Above all it is flexible, fast, high-performance, resilient, reliable, always available from anywhere on any device with a network access. Thus bringing people and systems together to work collaboratively in an environmentally sustainable manner across the cultural heritage value chain. The ultimate goal of our Eucrite cloud ecosystem offering and the proposed research efforts is to significantly reduce the cost and complexity of digitalisation of cultural heritage to drive research and innovation in a collaborative, open, and pre-competitive manner with deeper engagement of actors and stakeholders. To achieve this goal of democratisation of technology, our cloud solution also fosters unique personalised skill development with technology enhanced learning analytics and context-aware recommender system to stimulate interest for wider adaptation of these cutting-edge technologies all built into one Eucrite Cloud. In this WP we will develop necessary infrastructure, tools, products, solutions and services with by following a principle: create once, reuse everywhere so others do not have to reinvent the wheel and they can focus on solving their problems as against fiddling with the complex cloud computing technologies. 
\par

