\textbf{Description of work}\\
\task{5.1}{D1}{M1}{Workshop on Novel Diagnostic Techniques}{DEB}{IEP}{30}{34}\\
In this task we will deliver a training program for teachers and trainers who will learn to identify and analyse training needs of students. They will also learn to design and develop appropriate learning programs, deliver them and evaluate their effectiveness using the protocols developed in the WP1. Participants of this workshop will gain in depth knowledge of the tools, techniques and software used. This way participants shall holistically understand what goes in creating and delivering a successful training program.

\task{5.2}{D1}{}{Workshop Bosnian Cultural Heritage}{BAS}{DEB}{22}{34}\\
In this task we will deliver monthly student activities. Efforts of these knowledge transfer activities carried out in this task will be primarily targeted towards young girls and young adults. These activities will involve hands on onsite as well as online training to impart new cognitive skills. In order to engage with the public at large we will also target various school systems in Germany, Poland and the Netherlands.

\task{5.3}{D1}{}{Workshop Bohemian Agricultural Heritage}{CZU}{DEB}{22}{34}\\
In this task various team meetings will be organised to create the opportunity for knowledge transfer as well as to enhance the creative potential of the project team. Real-life meetings are preferred, nevertheless, hybrid meetings (i.e. partly real-life and online) are also taken into account due to the pandemic experience.

\task{5.4}{D1}{}{Workshop on Slovakian Cultural Heritage}{SKB}{DEB}{22}{34}\\
This task will host a week long workshop at SKB.

\task{5.5}{D1}{}{Workshop on Italian Cultural Heritage}{ITR}{DEB}{22}{34}\\
This task will host a week long workshop at ITR and ITV.

\task{5.6}{D1}{}{Workshop on Innovations in Exhibitions}{HUM}{DEB}{22}{34}\\
This task will host a week long workshop at HUM.

\task{5.7}{D1}{}{Workshop on European Cultural Heritage}{DEB}{CZU, SKB}{28}{34}\\
This task will host a week long workshop at DEB.


