\textbf{Description of work}\\
\task{6.1}{D1}{M1}{Progress Monitoring, Reporting, and Organisation of Events}{DEB}{CZU, SKB}{1}{22}\\
In order to co-ordinate collaboration between partners, online and face-to-face meetings, as well as telephonic conversations will be organised. Exchange of knowledge, materials, datasets and results will be ensured to secure project goals on time. The status of work programmes from work packages will be collected and combined in reports. Project progress will be reported to relevant stakeholders at regular intervals including to EU. Organise dissemination and communication by coordination of joint-publications, patents, presentations, workshops and summer school coordination. This task will ensure a set-up of online platform for the smooth working of various experimental and analytical activities. Reports on the quarterly project progress, status updates, project meetings, exchange with partners, supports, governmental bodies, and supporters. Reports on publications, patent applications, presentations, workshops. etc. will be performed.

\task{6.2}{D1}{}{Finance and Operation Management}{CZU}{DEB}{1}{22}\\
Team CZU will focus on delivering the objectives stated in this task title.

\task{6.3}{}{}{Membership Management}{SKB}{DEB}{1}{22}\\
Team SKB will focus on delivering the objectives stated in this task title.

\task{6.4}{}{}{Knowledge Management}{IED}{DEB}{1}{22}\\
Team IED will focus on delivering the objectives stated in this task title.

\task{6.5}{}{}{Technology Management}{DEB}{BEL, CZU, IED, SKB}{1}{22}\\
Team DEB will focus on delivering the objectives stated in this task title.

\task{6.6}{}{}{Project closure and finalreport}{DEB}{CZU}{1}{22}\\
All administrative work will be performed to close the project as per EU regulations.


